---
title: "Homework 3"
author: "Anthony Stachowski"
date: "9/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Assignment 3

The NBA has been interesting lately. Use the following page as a jumping point:

https://www.espn.com/nba/schedule/_/date/20200910

This page contains links with a gameID -- you will need those. Take those gameID values and scrape the play-by-play tables for each of the games on that main page. 

The ideal return is going to be each game having a complete data frame.


#### Assemble a list of links for the games on the above page:
```{r}

library(rvest)
library(magrittr)

espnLink = "https://www.espn.com/nba/schedule/_/date/20200910"

nbaLinks = read_html(espnLink) %>% 
  html_nodes("a[href*='nba/game?gameId=']") %>% 
  html_attr("href")  %>% 
  unique() %>% 
  paste("https://www.espn.com", ., sep = "")

```

#### Assemble a list of play-by-play links:
```{r}

pbpLinks = lapply(nbaLinks, function(link) {
  read_html(link) %>%
  html_nodes("a[href*='/nba/playbyplay?gameId=']") %>%
  html_attr("href") %>%
  unique() %>%
  paste("https://www.espn.com", ., sep = "")
})

```

#### Get play-by-play details by game:
```{r}

for(i in 1:length(pbpLinks)){
  
  Sys.sleep(sample(1:10, 1))
  dataList = list()
  
  pbpRead = read_html(pbpLinks[[i]])
  
  pbpBoxScore = pbpRead %>%
    html_table(fill = TRUE) %>%
    '[['(1)
  
  name = paste(pbpBoxScore[1,1],
               "_",
               pbpBoxScore[1,length(pbpBoxScore)],
               "-",
               pbpBoxScore[2,1],
               "_",
               pbpBoxScore[2,length(pbpBoxScore)],
               sep = "")
  
  for(t in 2:(ncol(pbpBoxScore)-1)){
    Sys.sleep(sample(1:5, 1))
    pbpQuarter = pbpRead %>%
      html_table(fill = TRUE) %>%
      '[['(t)
    pbpQuarter$quarter = t-1
    dataList[[t]] = pbpQuarter
  }
  
  assign(name, do.call(rbind, dataList))
}

```

#### View Data Frames:
```{r}
# View LAL at DEN play-by-play from September 10th:
`LAL_110-HOU_100`

# View DEN at LAC play-by-play from September 11th:
`DEN_111-LAC_105`

# View BOS at TOR play-by-play from September 11th:
`BOS_92-TOR_87`

# View HOU at LAL play-by-play from September 12th:
`HOU_96-LAL_119`

# View LAC at DEN play-by-play from September 13th:
`LAC_98-DEN_111`

# View MIA at BOS play-by-play from September 15th:
`MIA_117-BOS_114`

# View DEN at LAC play-by-play from September 15th:
`DEN_104-LAC_89`
```

